### 2025-07-23 basic-statistics.qmd
20250708 - track chunk execution times
20250717 - Conclusion sections
20250723 - interpretation

@@

@@

where $B_x$ is the unstandardized regression coefficient of the [predictor variable](#sec-correlationalStudy) $x$ in predicting the [outcome variable](#sec-correlationalStudy) $y$, $s_x$ is the standard deviation of $x$, and $s_y$ is the standard deviation of $y$.

>>>>

This chapter provides an overview of foundational statistical concepts.

@@

Cohen's $d$ is interpreted as the mean of group 1 was _ standard deviation units [larger/smaller] than the mean of group 2.

@@

where $B_x$ is the unstandardized regression coefficient of the [predictor variable](#sec-correlationalStudy) $x$ in predicting the [outcome variable](#sec-correlationalStudy) $y$, $s_x$ is the standard deviation of $x$, and $s_y$ is the standard deviation of $y$.
The standardized regression coefficient is interpreted such that, for every 1 standard deviation increase in $x$, there was a _ standard deviation [increase/decrease] in $y$.
